Towards a standardized evaluation of multiple imputation routines

### 2022-01-27 Manuscript/StandardizedEvaluation.Rmd
Add small simulation to manuscript

---
title: "Towards a standardized evaluation of multiple imputation routines"
author: "Hanne Oberman and Gerko Vink"
date: "19-1-2022"
abstract: "Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In this paper I propose a move towards a standardized evaluation of imputation methods. To demonstrate the need for standardization, I highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines. This may lead to suboptimal use of multiple imputation in practice. Additionally, I suggest a course of action for simulating and evaluating missing data problems."
bibliography: StandardizedEvaluation.bib  
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

>>>>

---
title: "Towards a standardized evaluation of multiple imputation routines"
author: "Hanne Oberman and Gerko Vink"
date: "19-1-2022"
abstract: "Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In this paper I propose a move towards a standardized evaluation of imputation methods. To demonstrate the need for standardization, I highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines. This may lead to suboptimal use of multiple imputation in practice. Additionally, I suggest a course of action for simulating and evaluating missing data problems."
bibliography: StandardizedEvaluation.bib  
output: pdf_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source(here::here("R/utils.R"))
source(here::here("R/run_sim.R"))
```

@@

```{r sim_mech, echo=FALSE, cache=TRUE, paged.print=TRUE}
# setup
set.seed(1)
n_sim <- 10
correlations <- c(0, .4, .8)
mechanisms <- c("MCAR", "MAR", "MNAR")

sim_mech <- purrr::map_dfr(1:n_sim, function(.i){
   purrr::map_dfr(correlations, function(.c){
     purrr::map_dfr(mechanisms, function(.m){
       run(corr = .c, mis_mech = .m) %>% cbind(sim = .i, .)})})})
sim_mech %>% 
  group_by(mis_mech, corr) %>% 
  summarise(
    mean_cca = mean(mean_cca - 10),
    mean_est = mean(mean_est - 10),
    beta_cca = mean(beta_cca - corr),
    beta_est = mean(beta_est - corr),
    beta_ciw = mean(beta_ciw),
    beta_cr = mean(beta_cr),
    rmse_pred = mean(rmse_pred),
    rmse_cell = mean(rmse_cell))
```

@@

```{r}
sessionInfo()

```
